Figures

### 2018-05-24 scripts/analysis.Rmd
include conceptual figure

@@

```{r fig.cap="Connectivity metric definitions and examples of high and low connectivity lakes.", echo=FALSE}
knitr::include_graphics("../figures/conny_metric_key_crop.pdf")
```

>>>>

```{r fig.cap="Major lake and watershed characteristics, factors, and processes affecting lake P retention. Shaded symbols indicate items typically considered in P retention models while open symbols indicate additional items considered in the present study.", echo=FALSE}
knitr::include_graphics("../figures/conceptual_p-cycle.pdf")
```

```{r fig.cap="Connectivity metric definitions along with examples of high and low connectivity lakes.", echo=FALSE}
knitr::include_graphics("../figures/conny_metric_key_crop.pdf")
```

@@
